---
title: "Merge HTML Data And Excel Data"
author: "Hiroaki Yutani"
date: "`r Sys.Date()`"
output: html_document
---

**Due to encoding problem, this Rmd cannot be knitted by "Knit" button**

```{r}
library(kokudosuuchiUtils)
packageDescription("kokudosuuchiUtils")$Built
```

```{r}
library(dplyr, warn.conflicts = FALSE)
```

Read data
---------

### Data from HTML files

```{r}
html_data <- readr::read_csv(rprojroot::find_package_root_file("inst/extdata/zokusei.csv"))

colnames(html_data) <-(c("identifier", "table_num", "name", "description", "type"))
html_data <- html_data %>%
  # remove rows without types
  filter(!is.na(.data$type)) %>%
  # remove description
  select(-.data$description)
```

### Data from Excel file

```{r}
excel_data <- readr::read_csv(rprojroot::find_package_root_file("inst/extdata/shape_property_table_xls.csv"))
```


Do some workarounds
-------------------

### `N05_005b` and `N05_005e` are crammed into one cell

See https://github.com/yutannihilation/kokudosuuchiUtils/issues/3#issuecomment-327374894

```{r}
indices_double_code <- html_data$name == "設置期間（設置開始）(N05_005b)設置期間（設置終了）(N05_005e)"
html_data_part_double_code <- html_data[indices_double_code, ] %>%
  mutate(name = stringr::str_split(.data$name, "(?<!^)(?=設置期間)")) %>%
  tidyr::unnest(.data$name)

html_data <- bind_rows(html_data[!indices_double_code, ],
                       html_data_part_double_code)
```

Separate codes into name, code and notes
----------------------------------------

```{r}
linebreak_pattern <- "\\s*[\\n\\r]+\\s*"
comment_pattern <- "(?<=[\\)）])[^\\(（]+$"

html_data <- html_data %>%
  # remove unneeded rows
  filter(!is.na(.data$type)) %>% 
  mutate(name = stringr::str_replace_all(.data$name, linebreak_pattern, "")) %>%
  # insert separators
  mutate(name = stringr::str_replace(.data$name,
                                     "([\\(（][A-Z][0-9a-z\\-]+[\\*※]?[_\\-][A-Za-z0-9\\-_ 〜]+[\\)）])", 
                                     "%NINJA%\\1%NINJA%")) %>%
  # separate by the separators
  tidyr::separate(col = .data$name,
                  into = c("name", "code", "note"),
                  sep = "%NINJA%",
                  fill = "right") %>%
  # clean up codes
  mutate(code = stringr::str_replace_all(code, "[（\\(）\\)\\*※]", ""),
         note = stringr::str_trim(note),
         note = dplyr::if_else(note == "", NA_character_, note))
```

Do some workarounds again
-------------------------

### Tilda

(See [Extract Attribute Names And Codes](../design/extract-code-name-note-from-attributes.md))

Tilda represents a sequence of numbers like:

```
P16_015～026
P17_006～
```

We need to translate this to the corresponding sequence of codes like:

```
P16_015
P16_016
P16_017
...
```

(Be careful: "〜"(`\u301c`) is not "~" or "～"(`\uff5e`).)

```{r}
indices_tilda <- dplyr::coalesce(stringr::str_detect(html_data$code, "〜"), FALSE)

# extract tilda
html_data_part_tilda <- html_data[indices_tilda, ] %>%
  # trim numbers from name
  mutate(name = stringr::str_replace(.data$name, "（?\\d+[\\-〜][\\dn]+）?", "")) %>% 
  # e.g. P16_015～026 -> prefix: P16, begin: 015, end: 026
  tidyr::separate(code, into = c("prefix", "begin", "end"), regex = "_|〜", fill = "right") %>%
  mutate_at(c("begin", "end"), funs(readr::parse_integer)) %>%
  # fill NAs with appropriate end numbers
  mutate(end = dplyr::coalesce(.data$end, 30L)) %>% 
  # expand rows
  mutate(code = purrr::pmap(., function(prefix, begin, end, ...) sprintf("%s_%03d", prefix, seq(begin, end)))) %>%
  tidyr::unnest(.data$code) %>%
  # add sequencial numbers to names (e.g. 備考 -> 備考1, 備考2, ...)
  group_by(identifier) %>%
  mutate(name = paste0(name, row_number())) %>%
  # we don't need prefix, begin and end anymore
  select(-(prefix:end))
```

```{r}
html_data_part_tilda
```

```{r}
html_data <- bind_rows(html_data,
                       html_data_part_tilda)
```

### `XX`

`XX` represents prefecture codes. But the codes with this seems only used for layer names, not for property names. So we ignore this here.

```{r}
html_data <- html_data %>%
  filter(!coalesce(stringr::str_detect(.data$code, "(?<=[^X])XX$"), FALSE))
```

### `XXXX`

`XXXX` represents year and needs special considerations. We ignore this here.

```{r}
html_data <- html_data %>%
  filter(!coalesce(stringr::str_detect(.data$code, "(?<=[^X])XXXX$"), FALSE))
```

Write intermediate data
-----------------------

```{r}
readr::write_csv(html_data, rprojroot::find_package_root_file("inst/extdata/html_data.csv"))
```
